### 2016-06-30 ch02-qlogms/excitation-design.tex
Move guideline 2.3
Address some smaller requests

In \figref{fig:excitation:coupling} the largest element in $\partial G_{1,2}$ is plotted for different dampings and separations. It is clear that highly resonant systems have a large degree of decoupling and that resonances that are well-separated increases the decoupling. 
The diagonal blocks of the normalized $\Fi{\theta}$ in all cases have some elements close to $1$. 
In this example, the $\damping$ is set to be the same in both sub-systems. 
%TODO: !! (EG) Comment on that this is not a requirement
Using different dampings in the sub-systems would, however, not change the argument, the systems with the lowest damping will limit the separation.

@@

  Finally, $\C_{X}$ denotes the covariance matrix of $X\left(\omega\right) = G\left(\omega, \theta_0 \right) - \frac{Y_0\left(\omega \right) + E\left( \omega \right)  }{ U\left( \omega \right) } $, evaluated at the excited frequencies $\omega_{\excited}$.
  By assuming that the $X\left( \omega \right) $ are independently distributed over the frequency $\omega$, the variance-covariance matrix $\C_{X}$ is a diagonal matrix \citep{Pintelon2012}:
  \begin{equation}
    \C_{X} =
               \left[ \left.
               \begin{matrix}
                 \frac{\sigma^2_E\left(\omega_1 \right) }
                      {\abs{ U\left(\omega_1 \right)}^2 } & \deemph{0} & \deemph{0}\\
                 \deemph{0} & \ddots & \deemph{0} \\
                 \deemph{0} & \deemph{0} & \frac{\sigma^2_E\left(\omega_F \right) }
                              {\abs{U\left(\omega_F \right)}^2 }
               \end{matrix}
               \right.^{\vphantom{x}}\right]
    \text{.}
  \end{equation}
  \begin{remark}
  To introduce only limited prior knowledge into the input design, we shall assume that the noise is white.
  Hence, $\sigma^2_E(\omega) = \sigma^2_E$ is constant over the whole frequency band of interest.
  If the noise coloring is known beforehand (or measured in a previous experiment), the design can be adapted in a straightforward manner.
  \end{remark}

>>>>

In \figref{fig:excitation:coupling} the largest element in $\partial G_{1,2}$ is plotted for different dampings and separations. It is clear that highly resonant systems have a large degree of decoupling and that resonances that are well-separated increases the decoupling. 
The diagonal blocks of the normalized $\Fi{\theta}$ in all cases have some elements close to $1$. 
In this example, the $\damping$ is set to be the same in both sub-systems. 
Using different dampings in the sub-systems would, however, not change the argument, as the sub-systems with the lowest damping will be the limiting factor.

@@

  Finally, $\C_{X}$ denotes the covariance matrix of $X\left(\omega\right) = G\left(\omega, \theta_0 \right) - \frac{Y_0\left(\omega \right) + E\left( \omega \right)  }{ U\left( \omega \right) } $, evaluated at the excited frequencies $\omega_{\excited}$.
  By assuming that the $X\left( \omega \right) $ are independently distributed over the frequency $\omega$, the variance-covariance matrix $\C_{X}$ is a diagonal matrix \citep{Pintelon2012}:
  \begin{equation}
    \C_{X} =
               \left[ \left.
               \begin{matrix}
                 \frac{\sigma^2_E\left(\omega_1 \right) }
                      {\abs{ U\left(\omega_1 \right)}^2 } & \deemph{0} & \deemph{0}\\
                 \deemph{0} & \ddots & \deemph{0} \\
                 \deemph{0} & \deemph{0} & \frac{\sigma^2_E\left(\omega_F \right) }
                              {\abs{U\left(\omega_F \right)}^2 }
               \end{matrix}
               \right.^{\vphantom{x}}\right]
    \text{.}
  \end{equation}
  \begin{remark}
  To introduce only limited prior knowledge into the input design, we shall assume that the noise is white.
  Hence, $\sigma^2_E(\omega) = \sigma^2_E$ is constant over the whole frequency band of interest.
  If the noise coloring is known beforehand (or measured in a previous experiment), the design can be adapted in a straightforward manner, e.g. by coloring the amplitude spectrum accordingly.
  \end{remark}
